---
title: "R Notebook"
output: html_notebook
---

```{r}
library(tidyverse)
library(ggimage)
library(lubridate)

emperors <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-08-13/emperors.csv")

emperors <- emperors %>% select(c(index, reign_start, reign_end, birth, death), everything())
emperors$name_full[[43]] <- "CAESAR MARCVS CLAVDIVS TACITVS AVGVSTVS"

for (i in seq(8, 12)) {
  emperors[[i]] <- factor(x = emperors[[i]], levels = unique(emperors[[i]]))
}

for (i in seq(13, 14)) {
  emperors[[i]] <- factor(x = emperors[[i]], levels = unique(emperors[[i]]), ordered=TRUE)
}
bce = c("Augustus", "Claudius", "Tiberius", "Galba")

years_asno <- emperors %>%
  mutate_if(is.Date, list(year = year)) %>%
  mutate(birth_year = if_else(name %in% bce, -birth_year, birth_year),
         reign_start_year = if_else(name == "Augustus", -reign_start_year, reign_start_year))

emperors <- emperors %>% mutate(reign_start_year = as.numeric(substr(reign_start, 1, 4))) %>%
  mutate(reign_end_year = as.numeric(substr(reign_end, 1, 4)))

emperors$reign_start_year[1] = -emperors$reign_start_year[1]

emperors <- emperors %>% 
     arrange(reign_start_year, index) %>%
     mutate(index, row_number())

name_count <- function(name_col){
  all_names <- unlist(strsplit(name_col, " ")) #  
  freq_df = as.data.frame(table(all_names))
  names(freq_df)[1] = "name_full"
  return(freq_df)
}

freq_df <- name_count(emperors$name_full)

#name_rank <- function(name_col){
#  idx_count <- list()
#  for (fname in name_col) {         
#    fname <- unlist(strsplit(fname, " "))
#    for (name in fname) {
#      ix = which(fname == name)
#      if (!(name %in% names(idx_count))) {
#        idx_count[[name]] <- c(ix, 1)
#      } else {
#        if (ix %in% idx_count$name[1]) {
#          idx_count$name[2][which(idx_count$name[1] == ix)] <- idx_count$name[2][which(idx_count$name[1] == ix)] + 1
#        } else {
#          idx_count$name[[1]] <- append(idx_count$name[[1]], ix)
#          idx_count$name[2][which(idx_count$name[1] == ix)] <- 1}
#      }
#    }
#  }  
#  return(idx_count)
#}

#n <- name_rank(emperors$name_full)
```

```{r}
killers <- emperors %>% group_by(killer) %>%
     summarise(no = length(killer))

emperors %>% group_by(cause) %>%
     summarise(no = length(cause))


```


```{r}
to_plot <- years_asno %>%
  filter(!is.na(birth_year))

by_dynasty <- to_plot %>%
  group_by(dynasty) %>%
  summarise(reign_start_year = min(reign_start_year),
            reign_end_year = max(reign_end_year))

big_pic <- ggplot(to_plot, aes(y=0)) +
  geom_segment(aes(x=reign_start_year, xend=reign_end_year,
                   yend=0)) +
# scale_color_manual("Dynasty", values = roman_palette, breaks =  names(roman_palette)) +
scale_x_continuous(breaks = c(-62, 0, 100, 200, 300, 400), labels = c("62 BC", "1 AD", "100 AD", "200 AD", "300 AD", "400 AD")) +
# expand_limits()
labs(x=NULL, y=NULL, caption="Roman Emperors")

bars <- ggplot(to_plot, aes(y=reorder(name, reign_start_year)))
   
```


write <- function(vector) {
    for (book in vector) {
        fileconn <- file(paste("book",toString(i),".txt"))
        for (i in length(book)) {
            writeLines(vector[i], fileconn)
            }
        close(fileconn)
    }
}

booksvec <- list(philosophers_stone, chamber_of_secrets, prisoner_of_azkaban, goblet_of_fire, order_of_the_phoenix, half_blood_prince, deathly_hallows)

writeBook <- function(book, num) {
  fileconn <- file(paste("book",toString(num),".txt"))
  writeLines(book, fileconn)
  close(fileconn)
    }